\textbf{Response Letter}

### 2018-12-02 doc/aij18/major-revision/letter.tex
addressed comments reviewer #2 to Intro

\begin{itemize}
\item \textbf{Introduction}. We performed a profound revision of the Introduction in order to make it more self-explanatory. First, we carefully revised all of the comments pointed by reviewer \#2. Additionally, as indicated by reviewer \#1, we provide at the end of the section the overall picture of our approach. Our modification is intended to adequately position our contribution within the concerned research field, and to provide a global picture of the \FAMA approach that explains our pursued objective.

@@

\item \textbf{Compilation scheme}. Reviewers \#1 and \#3 show several concerns about the understanding of section 4.4., the compilation approach. We acknowledge their concerns and we have thus introduced an introductory explanatory subsection that explains .......... before going into the technical details. We hope this new subsection will help the reader to have first a broad view of the compilation scheme before diving into the technicalities.

\end{itemize}

@@

We agree with the reviewer that we should provide ....

@@

As per the reviewer's recommendation, we requested the code of LOUGA to the first author of the publication entitled \emph{LOUGA: learning planning operators using genetic algorithms}, which was published in the Pacific Rim Knowledge Acquisition Workshop. The author of LOUGA promptly provided us with the code, so we would first like to thank him for his gentle response. However, the issue we faced with LOUGA is that we were not able to automate the processing and output of the results. LOUGA throws results in a graphical interface, which makes it hard to easily retrieve the data to be subsequently processed. Since the input of our automated process for extracting the experimental results are plain text files, we could not adapt the graphical output of LOUGA to our required input. Nevertheless, we did test a couple of ....

@@

\begin{mdframed}[hidealllines=true,backgroundcolor=gray!20]
  There are several cases where authors repeat themselves several times. Here are a few examples:

-          (page 2) "While current learning systems …. none of them allow partial observability in the sequence of executed actions "

@@

" … unlike most relevant action-model learning algorithms, FAMA does not require the traces to contain any observed action …"

(Page 8) "FAMA represents one step ahead … without assuming observed actions."

@@

\begin{mdframed}[hidealllines=true,backgroundcolor=gray!20]
  Surprisingly, adding more traces causes the precision and recall of FAMA to drop for the NO action NO states setting. The authors say this is because more timeouts were observed due to the complexity of the model learning planning problem. To support this, the authors should report the number of timeouts for the different number of traces. In particular, since we do not see this drop in precision and recall in the other settings, I expect a comparison of the number of timeouts as a function of the number of traces for both settings. If we see that the number of timeouts for this setting is larger than the simpler setting, that would support the authors conclusion.

\end{mdframed}

@@

\begin{mdframed}[hidealllines=true,backgroundcolor=gray!20]
    Page 1. "… an abstract version of the capability model that reflects … " – I am not sure that "abstract" is the right term here, since the learned model is not an abstraction of the real-world but an approximation of it.
\end{mdframed}

\begin{mdframed}[hidealllines=true,backgroundcolor=gray!20]
    Page 1.  "Two different types of data are generally identified in the generation of explanations … (2) data that do not accurately represent the decision-making process because the observed external behavior of the agent responds to a black-box model." – First, I think you meant "corresponds" and not "responds". Second, if the agent is treated as a black box, then this is not really a way to generate explanation. Please better explain the text after (2) .
\end{mdframed}

\begin{mdframed}[hidealllines=true,backgroundcolor=gray!20]
      Page 2. "… the synthesis of different kinds of generative models with classical planning …" – I do not understand this sentence. What do you mean by generative models in this context?
\end{mdframed}

\begin{mdframed}[hidealllines=true,backgroundcolor=gray!20]
      Page 2. "FAMA is a solving scheme … " – FAMA is a learning scheme, not a solving scheme. I agree that it is a learning scheme that learns by solving a planning problem.
\end{mdframed}

\begin{mdframed}[hidealllines=true,backgroundcolor=gray!20]
      Page 2. "… by the input observed actions, …" – What is "input observed actions"? please rephrase.
\end{mdframed}

\begin{mdframed}[hidealllines=true,backgroundcolor=gray!20]
      Page 3. "… the open world assumption" – Either explain what this means or provide a reference.
\end{mdframed}

>>>>

\begin{enumerate}
\item \textbf{Introduction}. We performed a profound revision of the Introduction in order to make it more self-explanatory. First, we carefully revised all of the comments pointed by reviewer \#2. Additionally, as indicated by reviewer \#1, we provide at the end of the section the overall picture of our approach. Our modification is intended to adequately position our contribution within the concerned research field, and to provide a global picture of the \FAMA approach that explains our pursued objective.

@@

\item \textbf{Compilation scheme}. Reviewers \#1 and \#3 show several concerns about the understanding of section 4.4., the compilation approach. We acknowledge their concerns and we have thus introduced an introductory explanatory subsection that explains .......... before going into the technical details. We hope this new subsection will help the reader to have first a broad view of the compilation scheme before diving into the technicalities.
\end{enumerate}

\textcolor{blue}{In the following, our responses to the reviewers are shown up in blue color.}

@@

\textcolor{blue}{We agree with the reviewer that we should provide ....}

@@

\textcolor{blue}{As per the reviewer's recommendation, we requested the code of LOUGA to the first author of the publication entitled \emph{LOUGA: learning planning operators using genetic algorithms}, which was published in the Pacific Rim Knowledge Acquisition Workshop. The author of LOUGA promptly provided us with the code, so we would first like to thank him for his gentle response. However, the issue we faced with LOUGA is that we were not able to automate the processing and output of the results. LOUGA throws results in a graphical interface, which makes it hard to easily retrieve the data to be subsequently processed. Since the input of our automated process for extracting the experimental results are plain text files, we could not adapt the graphical output of LOUGA to our required input. Nevertheless, we did test a couple of .... FALTA POR COMPLETAR}

@@

\begin{mdframed}[hidealllines=true,backgroundcolor=gray!20]
Repetitions.

  There are several cases where authors repeat themselves several times. Here are a few examples:
- (page 2) "While current learning systems …. none of them allow partial observability in the sequence of executed actions "

@@

" ... unlike most relevant action-model learning algorithms, FAMA does not require the traces to contain any observed action ..."

(Page 8) "FAMA represents one step ahead ... without assuming observed actions."

@@

\begin{mdframed}[hidealllines=true,backgroundcolor=gray!20]
  Surprisingly, adding more traces causes the precision and recall of FAMA to drop for the NO action NO states setting. The authors say this is because more timeouts were observed due to the complexity of the model learning planning problem. To support this, the authors should report the number of timeouts for the different number of traces. In particular, since we do not see this drop in precision and recall in the other settings, I expect a comparison of the number of timeouts as a function of the number of traces for both settings. If we see that the number of timeouts for this setting is larger than the simpler setting, that would support the authors conclusion.
\end{mdframed}

@@

\textcolor{blue}{We acknowledge the reviewer's concern and refer the reviewer to the main modification \#1 exposed at the beginning of this response letter.}
\vspace{0.1cm}

\begin{mdframed}[hidealllines=true,backgroundcolor=gray!20]
    Page 1. " an abstract version of the capability model that reflects ... " -- I am not sure that "abstract" is the right term here, since the learned model is not an abstraction of the real-world but an approximation of it.
\end{mdframed}

\textcolor{blue}{We have replaced the word 'abstract' by 'approximation' and rephrased the sentence a little bit.}
\vspace{0.1cm}

\begin{mdframed}[hidealllines=true,backgroundcolor=gray!20]
    Page 1.  "Two different types of data are generally identified in the generation of explanations … (2) data that do not accurately represent the decision-making process because the observed external behavior of the agent responds to a black-box model." -- First, I think you meant "corresponds" and not "responds". Second, if the agent is treated as a black box, then this is not really a way to generate explanation. Please better explain the text after (2) .
\end{mdframed}

\textcolor{blue}{We have rephrased the paragraph related to the two data sources used in explainable AI (XAI). Our intention is to set an analogy between the introspection/externality of data used in XAI with the data used in action-model learning systems}
\vspace{0.1cm}

\begin{mdframed}[hidealllines=true,backgroundcolor=gray!20]
      Page 2. " ... the synthesis of different kinds of generative models with classical planning ..." -- I do not understand this sentence. What do you mean by generative models in this context?

      Page 2. "FAMA is a solving scheme ..." -- FAMA is a learning scheme, not a solving scheme. I agree that it is a learning scheme that learns by solving a planning problem.

      Page 2. " ... by the input observed actions, ... " What is "input observed actions"? please rephrase.
\end{mdframed}

\textcolor{blue}{We have rephrased (and highlighted in red) all the paragraphs and sentences pointed by the reviewer. With respect to the first comment, we attempt to make it clear that classical planning techniques can be used to generate a large variety of planning models, not only \strips\ models, and that these techniques underpin some relevant concepts that are also reusable in learning models when the behaviour of the agent is not available.}
\textcolor{blue}{With respect to the other two comments, besides using different expressions to refer to the two concepts, we have included some additional side explanations that we hope help understand the meaning of the sentences.}
\vspace{0.1cm}

\begin{mdframed}[hidealllines=true,backgroundcolor=gray!20]
      Page 3. " ... the open world assumption" – Either explain what this means or provide a reference.
\end{mdframed}
